Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-13 tensor/draft/draft-tensor-op.tex
[draft] proofread appendix A

Here we present those angular observables $J_i$ in $B\to K^* \bar\ell\ell$
in which tensor and scalar contributions are kinematically enhanced by a factor
$\sqrt{q^2}/m_\ell$ over vector once present in the SM or their respective
interference terms using results and notation from \cite{Bobeth:2012vn}.

For convenience, we split the time-like transversity amplitude into
\begin{align}
  A_t &
  = \tilde{A}_t - \frac{1}{2} \frac{\sqrt{q^2}}{m_\ell} A_P
\end{align}
that depend on the Wilson coefficients $i = 10, 10', P, P'$ and the scalar
$B\to K^*$ form factor $A_0(q^2)$, a normalisation factor $N$ and the
K{\"a}ll{\'e}n-function $\lambda$ (see \cite{Bobeth:2012vn})
\begin{equation}
\begin{aligned}
  \tilde{A}_t & = 2 N \frac{\sqrt{\lambda}}{\sqrt{q^2}}
    (\wilson[]{10} - \wilson[]{10'}) A_0\,,
\\
  A_P & = - 2 N\sqrt{\lambda} \frac{(\wilson[]{P} - \wilson[]{P'})}{(m_b+m_s)} A_0\,.
\end{aligned}
\end{equation}
The lepton-flavor index $\ell$ at Wilson coefficients is omitted for
brevity throughout this section.

In full generality angular observables in $B\to K^* \bar\ell\ell$ depend on
seven transversity amplitudes with vector and dipole contributions
$A_{0,\,\perp,\,\parallel}^{L,R}$, and $\tilde{A}_t$, one scalar and one
pseudoscalar amplitude $A_{S,\,P} \propto (\wilson[]{S,P} - \wilson[]{S',P'})$,
and six tensor amplitudes: $A_{\parallel\perp,\,t\perp,\,0\parallel} \propto
\wilson[]{T}$ and $A_{t0,\,t\parallel,\,0\perp} \propto \wilson[]{T5}$.
The interesting combinations are
\begin{align}
  \frac{4}{3} J_{6c}  =
  4\, \beta_\ell\, \mbox{Re} \bigg[ &2\, (A_{t0}^{} A_S^* - A_{\parallel\perp}^{} A_P^*) \nonumber\\
  &+ \frac{m_\ell}{\sqrt{q^2}} \big[(A_0^L + A_0^R) A_S^*
           + 4\, A_{\parallel\perp}^{} \tilde{A}_t^* \big] \bigg],
\end{align}
\begin{align}
  \frac{4}{3}\(J_{1c} + J_{2c}\)  = \;
    &\Bigg| \frac{2\, m_\ell}{\sqrt{q^2}} (A_0^L + A_0^R) + 4\, A_{t0} \Bigg|^2 + \beta_\ell^2\, |A_S|^2 \nonumber\\
   + &\Bigg|\frac{2\, m_\ell}{\sqrt{q^2}}\, \tilde{A}_t - A_P\Bigg|^2
   + 16\, \beta_\ell^2\, |A_{\parallel\perp}|^2,
 \end{align}
 \begin{align}
 \frac{4}{3}\(J_{1s} - 3\, J_{2s}\) = \;
    &\Bigg| \frac{\sqrt{2}\, m_\ell}{\sqrt{q^2}} (A_\perp^L + A_\perp^R) + 4\, A_{t\perp} \Bigg|^2 \nonumber\\
  + &\Bigg| \frac{\sqrt{2}\, m_\ell}{\sqrt{q^2}} (A_\parallel^L + A_\parallel^R) + 4\, A_{t\parallel} \Bigg|^2.
\end{align}
Above $\beta_\ell^2 = 1 - 4 m_\ell^2/q^2 \to 1$ for $m_\ell \ll
\sqrt{q^2}$.  The condition is well fulfilled for $\ell = e$ and $1\,
\mbox{GeV}^2\lesssim q^2$, provided that tensor and scalar Wilson
coefficients do not receive additional suppression factors. For $\ell
= \mu$ the value of $q^2$ should not be too low, whereas in the case
$\ell = \tau$, these observables are not anymore dominated by tensor
and/or scalar contributions alone, and the full lepton-mass dependence
has to be taken into account.  Finally, we note that the term
\begin{align}
  &\Bigg|\frac{2\, m_\ell}{\sqrt{q^2}}\, \tilde{A}_t - A_P\Bigg|^2
   + \beta_\ell^2\, |A_S|^2   =  4 N^2 \lambda A_0^2 \Bigg\{
    \beta_\ell^2 \Bigg|\frac{\wilson[]{S} - \wilson[']{S}}{m_b + m_s}\Bigg|^2\nonumber\\
  &\hskip1cm + \Bigg|\frac{\wilson[]{P} - \wilson[']{P}}{m_b + m_s}
     + \frac{2 m_\ell}{q^2} \big(\wilson[]{10} - \wilson[']{10}\big) \Bigg|^2
    \Bigg\}
\end{align}
entering $(J_{1c} + J_{2c})$, resembles very much the branching ratio of the rare
decays $B_s \to \bar\ell\ell$ in the limit $q^2 \to M_{B_s}^2$
\begin{align}
\label{eq:Br-Bsmumu:time0}
  {\cal B}(B_s \to \bar\ell\ell) &=
    \frac{G_F^2 \alpha_e^2 |V_{tb}^{} V_{ts}^*|^2}{64\, \pi^3}
    M_{B_s}^5 f_{B_s}^2 \tau_{B_s} \beta_\ell(q^2 = M_{B_s}^2)
\nonumber\\
    & \times \Bigg\{
    \beta_\ell^2(q^2 = M_{B_s}^2) \Bigg|\frac{\wilson[]{S} - \wilson[']{S}}{m_b + m_s}\Bigg|^2 \nonumber\\
    &+ \Bigg|\frac{\wilson[]{P} - \wilson[']{P}}{m_b + m_s}
     + \frac{2 m_\ell}{M_{B_s}^2} \big(\wilson[]{10} - \wilson[']{10}\big) \Bigg|^2
    \Bigg\}\,.
  \end{align}
Hence there is some complementarity among $(J_{1c} + J_{2c})$ in $B \to K^*
\bar\ell\ell$ and ${\cal B}(B_s \to \bar\ell\ell)$, however former depends also
on tensor couplings and vector couplings. The helicity suppression
factor $4\,m_\ell^2/q^2$ of vector couplings is weaker in
$B \to K^* \bar\ell\ell$ decays than the corresponding factor
$4\,m_\ell^2/M_{B_s}^2$ in $B_s \to \bar\ell\ell$.

Concerning $B_s\to \bar\ell\ell$, the expression \refeq{eq:Br-Bsmumu:time0}
corresponds to the unintegrated branching ratio at time $t=0$. Due to the non-vanishing
decay width $\Delta\Gamma_s$, experiments measure the average
time-integrated branching ratio --- denoted by $\overline{\cal B}$ ---
and both are related as \cite{DeBruyn:2012wk}
\begin{align}
  \label{eq:Br-Bsmumu}
  \overline{\cal B} (B_s \to \bar\ell\ell) &
  = \frac{1 + y_s {\cal A}_{\Delta\Gamma}}{1 - y_s^2} {\cal B} (B_s \to \bar\ell\ell)\,.
\end{align}
Here $y_s \equiv \Delta\Gamma_s/(2\Gamma_s)$ with the numerical value given in
\cite{Beaujean:2013soa}. ${\cal A}_{\Delta\Gamma}$ is the CP asymmetry
due to nonvanishing width difference, which is ${\cal A}_{\Delta\Gamma} = 1$
in the SM, but in general can be ${\cal A}_{\Delta\Gamma} \in [-1,\, 1]$.
Since ${\cal A}_{\Delta\Gamma}$ can depart from it's SM value in scenarios of
new physics considered in this work, we take this effect into account
in our numerical analysis, although it is suppressed by small $y_s$. The latest
SM prediction $\overline{\cal B} (B_s \to \bar\mu\mu) = (3.65 \pm 0.23) \cdot
10^{-9}$~\cite{Bobeth:2013uxa} includes NLO electroweak \cite{Bobeth:2013tba}
and NNLO QCD corrections \cite{Hermann:2013kca}.

Finally we discuss the possibility of suitable normalisations of $J_{6c}$,
$(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$ at high $q^2$ that would provide
optimised observables. For this purpose we use form factor relations at leading
order in $1/m_b$ and neglect terms suppressed by $m_\ell/\sqrt{q^2}$. With the
notation and expressions derived in \cite{Bobeth:2012vn},
\begin{equation}
\begin{aligned}
  J_{1s} - 3\, J_{2s} & = \frac{3}{2}\, \rho_1^T (f_\perp^2 + f_\parallel^2) \,,
\\[0.1cm]
  J_{1c} + J_{2c} & = 3\, \rho_1^T f_0^2
     + \frac{3 N^2 \lambda}{(m_b+m_s)^2} A_0^2
\\
   & \quad \times \left(|\wilson{S}-\wilson{S'}|^2 + |\wilson{P}-\wilson{P'}|^2\right)\,.
%\\[0.1cm]
%  \frac{4}{3} J_{6c} & = \todo{???}
\end{aligned}
\end{equation}
Here $f_{\perp, \parallel, 0}$ and $A_0$ denote $B\to K^*$ form factors, whereas
the $\rho_1^\pm$ depends on vector couplings and $\rho_1^T \propto
(|\wilson{T}|^2 + |\wilson{T5}|^2)$.

Concerning $(J_{1s} - 3\, J_{2s})$, there are no appropriate normalisations,
unless chirality-flipped $\wilson[NP]{7',\,9',\,10'} = 0$ vanish, because then
$\rho_1^+ = \rho_1^-$ holds. There are three potential normalisations
\begin{equation}
\begin{aligned}
  \frac{4}{3} & J_{1s} =
    (3 \rho_1^+ + \rho_1^T) f_\perp^2 +  (3 \rho_1^- + \rho_1^T) f_\parallel^2 \,,
\\
  \frac{8}{3} & J_{2s} =
    (\rho_1^+ - \rho_1^T) f_\perp^2 +
    (\rho_1^- - \rho_1^T) f_\parallel^2 \,,
\\[0.1cm]
  & J_{1s} + 2 J_{2s} =
    3 (\rho_1^+ f_\perp^2 + \rho_1^- f_\parallel^2) \,
\end{aligned}
\end{equation}
where the last one depends only on vector couplings, i.e., is free of
tensor and scalar ones. In the $J_{1s}$ and $J_{2s}$, tensor couplings
contribute either cumulative or destructive to vector couplings in
$\rho_1^\pm$.

A similar situation arises for $(J_{1c} + J_{2c})$, where no appropriate
normalisation exists, unless scalar couplings vanish. In this special
case, either $J_{1c}$ and also $J_{2c} = -3/2 (\rho_1^- - \rho_1^T) f_0^2$ will
depend only on $f_0$ and can be used as normalisation. In the general case,
$J_{2c}$ still depends only on tensor couplings and was used at low $q^2$
\cite{Matias:2012xw}. Finally we note that
\begin{equation}
\begin{aligned}
  J_{1c} - J_{2c} & = 3\,\rho_1^- f_0^2 + \frac{3 N^2 \lambda}{(m_b+m_s)^2} A_0^2
\\
   & \quad \times \left(|\wilson{S}-\wilson{S'}|^2 + |\wilson{P}-\wilson{P'}|^2\right)\,.
\end{aligned}
\end{equation}
is free of tensor couplings at high $q^2$ and would provide access to
$\rho_1^-$ provided scalar couplings vanish.

>>>>

Here we focus on those angular observables $J_i$ in $B\to K^* \bar\ell\ell$ in
which tensor and scalar contributions are kinematically enhanced by a factor
$\sqrt{q^2}/m_\ell$ compared to the vector contributions of the SM or the
respective interference terms. The results and the notation follow
\cite{Bobeth:2012vn}.

For convenience, we split the time-like transversity amplitude $A_t$ into two
parts as
\begin{align}
  A_t &
  = \tilde{A}_t - \frac{1}{2} \frac{\sqrt{q^2}}{m_\ell} A_P \, .
\end{align}
Both terms depend on the scalar $B\to K^*$ form factor $A_0(q^2)$, a
normalization factor $N$, and the K{\"a}ll{\'e}n-function $\lambda$ (see
\cite{Bobeth:2012vn}) but have a different dependence on the Wilson coefficients
$i = 10, 10', P, P'$:
\begin{equation}
\begin{aligned}
  \tilde{A}_t & = 2 N \frac{\sqrt{\lambda}}{\sqrt{q^2}}
    (\wilson[]{10} - \wilson[]{10'}) A_0\,,
\\
  A_P & = - 2 N\sqrt{\lambda} \frac{(\wilson[]{P} - \wilson[]{P'})}{(m_b+m_s)} A_0\,.
\end{aligned}
\end{equation}
The lepton-flavor index $\ell$ of Wilson coefficients is omitted for brevity
throughout.

In full generality, the angular observables in $B\to K^* \bar\ell\ell$ depend on
seven transversity amplitudes with vector and dipole contributions,
$A_{0,\,\perp,\,\parallel}^{L,R}$ and $\tilde{A}_t$, one scalar and one
pseudoscalar amplitude, $A_{S,\,P} \propto (\wilson[]{S,P} - \wilson[]{S',P'})$,
and six tensor amplitudes, $A_{\parallel\perp,\,t\perp,\,0\parallel} \propto
\wilson[]{T}$ and $A_{t0,\,t\parallel,\,0\perp} \propto \wilson[]{T5}$.  The
interesting combinations are
\begin{align}
  \frac{4}{3} J_{6c}  =
  4\, \beta_\ell\, \mbox{Re} \bigg[ &2\, (A_{t0}^{} A_S^* - A_{\parallel\perp}^{} A_P^*) \nonumber\\
  &+ \frac{m_\ell}{\sqrt{q^2}} \big[(A_0^L + A_0^R) A_S^*
           + 4\, A_{\parallel\perp}^{} \tilde{A}_t^* \big] \bigg],
\end{align}
\begin{align}
  \label{eq:j1c-j2c}
  \frac{4}{3}\(J_{1c} + J_{2c}\) = \;
  &\Bigg| \frac{2\, m_\ell}{\sqrt{q^2}} (A_0^L + A_0^R) + 4\, A_{t0} \Bigg|^2    + 16\, \beta_\ell^2\, |A_{\parallel\perp}|^2 \nonumber\\
  + &\Bigg|\frac{2\, m_\ell}{\sqrt{q^2}}\, \tilde{A}_t - A_P\Bigg|^2 +
  \beta_\ell^2\, |A_S|^2,
 \end{align}
 \begin{align}
 \frac{4}{3}\(J_{1s} - 3\, J_{2s}\) = \;
    &\Bigg| \frac{\sqrt{2}\, m_\ell}{\sqrt{q^2}} (A_\perp^L + A_\perp^R) + 4\, A_{t\perp} \Bigg|^2 \nonumber\\
  + &\Bigg| \frac{\sqrt{2}\, m_\ell}{\sqrt{q^2}} (A_\parallel^L + A_\parallel^R) + 4\, A_{t\parallel} \Bigg|^2.
\end{align}
The function $\beta_\ell^2(q^2) \equiv 1 - 4 m_\ell^2/q^2$ tends to 1 for $m_\ell \ll
\sqrt{q^2}$.  This condition is well fulfilled for $\ell = e$ and $q^2 \gtrsim
1\, \mbox{GeV}^2$, provided that tensor and scalar Wilson coefficients do not
receive additional suppression factors. For $\ell = \mu$, the value of $q^2$
should not be too low, whereas in the case $\ell = \tau$, these observables are
not anymore dominated by tensor and scalar contributions alone, and the full
lepton-mass dependence has to be taken into account.  Finally, we note that the
second part of $(J_{1c} + J_{2c})$ in \refeq{eq:j1c-j2c},
\begin{align}
  &\Bigg|\frac{2\, m_\ell}{\sqrt{q^2}}\, \tilde{A}_t - A_P\Bigg|^2
   + \beta_\ell^2\, |A_S|^2   =  4 N^2 \lambda A_0^2 \Bigg\{
    \beta_\ell^2 \Bigg|\frac{\wilson[]{S} - \wilson[']{S}}{m_b + m_s}\Bigg|^2\nonumber\\
  &\hskip1cm + \Bigg|\frac{\wilson[]{P} - \wilson[']{P}}{m_b + m_s}
     + \frac{2 m_\ell}{q^2} \big(\wilson[]{10} - \wilson[']{10}\big) \Bigg|^2
    \Bigg\}\,,
\end{align}
 resembles very much the branching ratio of the rare
decay $B_s \to \bar\ell\ell$ in the limit $q^2 \to M_{B_s}^2$
\begin{align}
\label{eq:Br-Bsmumu:time0}
  {\cal B}(B_s \to \bar\ell\ell) &=
    \frac{G_F^2 \alpha_e^2 |V_{tb}^{} V_{ts}^*|^2}{64\, \pi^3}
    M_{B_s}^5 f_{B_s}^2 \tau_{B_s} \beta_\ell(q^2 = M_{B_s}^2)
\nonumber\\
    & \times \Bigg\{
    \beta_\ell^2(q^2 = M_{B_s}^2) \Bigg|\frac{\wilson[]{S} - \wilson[']{S}}{m_b + m_s}\Bigg|^2 \nonumber\\
    &+ \Bigg|\frac{\wilson[]{P} - \wilson[']{P}}{m_b + m_s}
     + \frac{2 m_\ell}{M_{B_s}^2} \big(\wilson[]{10} - \wilson[']{10}\big) \Bigg|^2
    \Bigg\}\,.
  \end{align}
  Hence there is some similarity between $(J_{1c} + J_{2c})$ in $B \to K^*
  \bar\ell\ell$ and ${\cal B}(B_s \to \bar\ell\ell)$ in their dependence on the
  couplings but the former has additional dependence on tensor and vector
  couplings through the other transversity amplitudes.  In $B \to K^*
  \bar\ell\ell$, the helicity suppression factor $4\,m_\ell^2/q^2$ of vector
  couplings is weaker than the corresponding factor $4\,m_\ell^2/M_{B_s}^2$ in
  $B_s \to \bar\ell\ell$.

  Concerning $B_s\to \bar\ell\ell$, the expression \refeq{eq:Br-Bsmumu:time0}
  corresponds to the unintegrated branching ratio at time $t=0$. Due to the
  non-vanishing decay width $\Delta\Gamma_s$, experiments measure the average
  time-integrated branching ratio---denoted by $\overline{\cal B}$---and the two
  are related as \cite{DeBruyn:2012wk}
\begin{align}
  \label{eq:Br-Bsmumu}
  \overline{\cal B} (B_s \to \bar\ell\ell) &
  = \frac{1 + y_s {\cal A}_{\Delta\Gamma}}{1 - y_s^2} {\cal B} (B_s \to \bar\ell\ell)\,.
\end{align}
Here $y_s \equiv \Delta\Gamma_s/(2\Gamma_s)$ with the numerical value given in
\cite{Beaujean:2013soa}. ${\cal A}_{\Delta\Gamma}$ is the CP asymmetry
due to nonvanishing width difference, which is ${\cal A}_{\Delta\Gamma} = 1$
in the SM, but in general can be ${\cal A}_{\Delta\Gamma} \in [-1,\, 1]$.
Since ${\cal A}_{\Delta\Gamma}$ can depart from it's SM value in scenarios of
new physics considered in this work, we take this effect into account
in our numerical analysis, although it is suppressed by small $y_s$. The latest
SM prediction $\overline{\cal B} (B_s \to \bar\mu\mu) = (3.65 \pm 0.23) \cdot
10^{-9}$~\cite{Bobeth:2013uxa} includes NLO electroweak \cite{Bobeth:2013tba}
and NNLO QCD corrections \cite{Hermann:2013kca}.

Finally we discuss the possibility of suitable normalisations of $J_{6c}$,
$(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$ at high $q^2$ that would provide
optimized observables. For this purpose we use form-factor relations at leading
order in $1/m_b$ and neglect terms suppressed by $m_\ell/\sqrt{q^2}$. With the
notation and expressions derived in \cite{Bobeth:2012vn},
\begin{equation}
\begin{aligned}
  J_{1s} - 3\, J_{2s} & = \frac{3}{2}\, \rho_1^T (f_\perp^2 + f_\parallel^2) \,,
\\[0.1cm]
  J_{1c} + J_{2c} & = 3\, \rho_1^T f_0^2
     + \frac{3 N^2 \lambda}{(m_b+m_s)^2} A_0^2
\\
   & \quad \times \left(|\wilson{S}-\wilson{S'}|^2 + |\wilson{P}-\wilson{P'}|^2\right)\,.
%\\[0.1cm]
%  \frac{4}{3} J_{6c} & = \todo{???}
\end{aligned}
\end{equation}
Here $f_{\perp, \parallel, 0}$ and $A_0$ denote $B\to K^*$ form factors, whereas
the $\rho_1^\pm$ depends on vector couplings and $\rho_1^T \propto
(|\wilson{T}|^2 + |\wilson{T5}|^2)$.

Concerning $(J_{1s} - 3\, J_{2s})$, there are no appropriate normalisations,
unless the chirality-flipped $\wilson[NP]{7',\,9',\,10'} = 0$ because then
$\rho_1^+ = \rho_1^-$ holds. There are three potential normalizations
\begin{equation}
\begin{aligned}
  \frac{4}{3} & J_{1s} =
    (3 \rho_1^+ + \rho_1^T) f_\perp^2 +  (3 \rho_1^- + \rho_1^T) f_\parallel^2 \,,
\\
  \frac{8}{3} & J_{2s} =
    (\rho_1^+ - \rho_1^T) f_\perp^2 +
    (\rho_1^- - \rho_1^T) f_\parallel^2 \,,
\\[0.1cm]
  & J_{1s} + 2 J_{2s} =
    3 (\rho_1^+ f_\perp^2 + \rho_1^- f_\parallel^2) \,
\end{aligned}
\end{equation}
where the last one depends only on vector couplings; i.e., is free of tensor and
scalar ones. In $J_{1s}$ and $J_{2s}$, tensor couplings contribute either
cumulatively or destructively to vector couplings in $\rho_1^\pm$.

A similar situation arises for $(J_{1c} + J_{2c})$, where no appropriate
normalization exists, unless scalar couplings vanish. In this special case, both
$J_{1c}$ and $J_{2c} = -3/2 (\rho_1^- - \rho_1^T) f_0^2$ depend only on $f_0$
and can be used as normalization. In the general case, $J_{2c}$ still depends
only on tensor couplings and was used at low $q^2$ \cite{Matias:2012xw}. Finally
we note that
\begin{equation}
\begin{aligned}
  J_{1c} - J_{2c} & = 3\,\rho_1^- f_0^2 + \frac{3 N^2 \lambda}{(m_b+m_s)^2} A_0^2
\\
   & \quad \times \left(|\wilson{S}-\wilson{S'}|^2 + |\wilson{P}-\wilson{P'}|^2\right)\,.
\end{aligned}
\end{equation}
is free of tensor couplings at high $q^2$ and would provide access to
$\rho_1^-$ provided scalar couplings vanish.
